%%% experience.ltx ---

%% Author:        Didier Verna <didier@lrde.epita.fr>
%% Maintainer:    Didier Verna <didier@lrde.epita.fr>
%% Created:       Sun May 23 22:04:41 1999 under XEmacs 21.2 (beta 12)
%% Last Revision: Mon Jul 12 12:03:38 1999


%%% Commentary:

%% Contents management by FCM version 0.1.

\begin{rubric}{P U B L I C A T I O N S}
% \subrubric{Articles dans des Revues Internationales:}
% \entry*[2008]
% P.~Doll\'ar, V.~Rabaud, G.~Cottrell and S.~Belongie, ``Behavior Recognition
% via Sparse Spatio-Temporal Features,'' {\em IEEE Transaction on Pattern
% Analysis and Machine Intelligence} (\textbf{PAMI, in preparation}), 2008.
\subrubric{Articles dans des Conf\'{e}rences Internationales:}
\entry*[2013]
A.~Ziegler, E.~Christiansen, V.~Rabaud, S.~Belongie, D.~Kriegman, ``Match-time covariance for 
descriptors'', \textbf{BMVC}, 2013.
\entry*[2013]
S.~Leutenegger, P.~T.~Furgale, V.~Rabaud, M.~Chli, K.~Konolige and R.~Siegwart, ``Keyframe-Based Visual-Inertial SLAM using Nonlinear Optimization.'', (\textbf{RSS}), 2013.
\entry*[2013]
M.~Dimashova, I.~Lysenkov, V.~Rabaud, V.~Eruhimov ``Tabletop Object Scanning with an RGB-D Sensor'' , 3rd Workshop 
on Semantic Perception, \textbf{ICRA}, 2013.
\entry*[2013]
I.~Lysenkov, V.~Rabaud, ``Pose Estimation of Rigid Transparent Objects in Transparent Clutter'' , 
(\textbf{ICRA}), 2013.
\entry*[2011]
E.~Rublee, V.~Rabaud, K.~Konolige and G.~Bradski, ``ORB: an efficient alternative to SIFT or SURF'' , {\em IEEE 
International Conference in Computer Vision}, (\textbf{ICCV}), 2011.
\entry*[2009]
V.~Rabaud and S.~Belongie, ``Linear Embeddings in Non-Rigid Structure from
Motion'' , {\em IEEE Conference on Computer Vision and Pattern Recognition},
(\textbf{CVPR}), 2009.
\entry*[2008]
V.~Rabaud and S.~Belongie, ``Re-Thinking Non-Rigid Structure From Motion'' ,
{\em IEEE Conference on Computer Vision and Pattern Recognition},
(\textbf{CVPR}), 2008.
\entry*[2007]
S.~Steinbach, V.~Rabaud and S.~Belongie, ``Soylent Grid: it's made of People !'' , {\em Interactive Computer Vision, in conjunction with ICCV}, (\textbf{ICV}), 2007.
\entry*[2007]
P.~Doll\'ar, V.~Rabaud and S.~Belongie, ``Non-Isometric Manifold Learning: Analysis and an Algorithm'', {\em International Conference on Machine Learning}, (\textbf{ICML}), 2007.
\entry*[2006]
P.~Doll\'ar, V.~Rabaud and S.~Belongie, ``Learning to Traverse Image Manifolds'' , {\em Neural Information Processing Systems}, (\textbf{NIPS}), 2006. 
\entry*[2006]
V.~Rabaud and S.~Belongie, ``Counting Crowded Moving Objects,'', {\em IEEE Conference on Computer Vision and Pattern Recognition}, (\textbf{CVPR}), 2006, pp. 705- 711, vol. 1.
\entry*[2005]
P.~Doll\'ar, V.~Rabaud, G.~Cottrell and S.~Belongie, ``Behavior Recognition via Sparse Spatio-Temporal Features,'' {\em Joint International Workshop on Visual Surveillance and Performance Evaluation of Tracking and Surveillance}, (\textbf{VS-PETS}), 2005. 
\entry*[2005]
S.~Belongie, K.~Branson, P.~Doll\'ar, and V.~Rabaud, ``Monitoring Animal Behavior in the Smart Vivarium,'' {\em International Conference on Methods and Techniques in Behavioral Research}, 2005.
\entry*[2005]
V.~Rabaud and S.~Belongie, ``Big Little Icons,'' {\em IEEE Workshop on Computer Vision Applications for the Visually Impaired, in conjunction with CVPR}, (\textbf{CVAVI}), 2005.
\entry*[2003]
K.\ Branson, V.\ Rabaud and S.\ Belongie, ``Three Brown Mice: See How They Run,''
{\em Joint International Workshop on Visual Surveillance and Performance Evaluation of Tracking and Surveillance}, (\textbf{VS-PETS}), 2003, pp.\ 78-85. 
\entry*[2003]
V.\ Rabaud and B.\ Deguine ``A Geometrical Approach To Determine Blackout Windows At Launch,''
AAS/AIAA Space Flight Mechanics Meeting, Ponce, Puerto Rico, (\textbf{AAS}), 2003, 03-187 
\end{rubric}


%%% Local Variables:
%%% TeX-master: cv.ltx
%%% ispell-local-dictionary: "francais"
%%% TeX-master: t
%%% End:

%%% experience.ltx ends here
