A.~Ziegler, E.~Christiansen, V.~Rabaud, S.~Belongie, D.~Kriegman, ``Match-time covariance for 
descriptors'', \textbf{BMVC}, 2013.

S.~Leutenegger, P.~T.~Furgale, V.~Rabaud, M.~Chli, K.~Konolige and R.~Siegwart, ``Keyframe-Based Visual-Inertial SLAM using Nonlinear Optimization.
'', (\textbf{RSS}), 2013.

M.~Dimashova, I.~Lysenkov, V.~Rabaud, V.~Eruhimov ``Tabletop Object Scanning with an RGB-D Sensor'' , 3rd Workshop 
on Semantic Perception, \textbf{ICRA}, 2013.

I.~Lysenkov, V.~Rabaud, ``Pose Estimation of Rigid Transparent Objects in Transparent Clutter'' , \textbf{ICRA}, 2013.

E.~Rublee, V.~Rabaud, K.~Konolige and G.~Bradski, ``ORB: an efficient alternative to SIFT or SURF'' , {\em IEEE 
International Conference in Computer Vision}, (\textbf{ICCV}), 2011.

V.~Rabaud and S.~Belongie, ``Linear Embeddings in Non-Rigid Structure from Motion'' , {\em IEEE Conference on Computer 
Vision and Pattern Recognition}, (\textbf{CVPR}), 2009.

V.~Rabaud and S.~Belongie, ``Re-Thinking Non-Rigid Structure From Motion'' , {\em IEEE Conference on Computer Vision and 
Pattern Recognition}, (\textbf{CVPR}), 2008.

S.~Steinbach, V.~Rabaud and S.~Belongie, ``Soylent Grid: it's made of People !'' , {\em Interactive Computer Vision, in 
conjunction with ICCV}, (\textbf{ICV}), 2007.

P.~Doll\'ar, V.~Rabaud and S.~Belongie`, ``Non-Isometric Manifold Learning: Analysis and an Algorithm'', {\em 
International Conference on Machine Learning}, (\textbf{ICML}), 2007.

P.~Doll\'ar, V.~Rabaud and S.~Belongie, ``Learning to Traverse Image Manifolds'' , {\em Neural Information Processing 
Systems}, (\textbf{NIPS}), 2006. 

V.~Rabaud and S.~Belongie, ``Counting Crowded Moving Objects,'', {\em IEEE Conference on Computer Vision and Pattern 
Recognition}, (\textbf{CVPR}), 2006, pp. 705- 711, vol. 1.

P.~Doll\'ar, V.~Rabaud, G.~Cottrell and S.~Belongie, ``Behavior Recognition via Sparse Spatio-Temporal Features,'' {\em 
Joint International Workshop on Visual Surveillance and Performance Evaluation of Tracking and Surveillance}, 
(\textbf{VS-PETS}), 2005. 

S.~Belongie, K.~Branson, P.~Doll\'ar, and V.~Rabaud, ``Monitoring Animal Behavior in the Smart Vivarium,'' {\em 
International Conference on Methods and Techniques in Behavioral Research}, 2005.

V.~Rabaud and S.~Belongie, ``Big Little Icons,'' {\em IEEE Workshop on Computer Vision Applications for the Visually 
Impaired, in conjunction with CVPR}, (\textbf{CVAVI}), 2005.

K.\ Branson, V.\ Rabaud and S.\ Belongie, ``Three Brown Mice: See How They Run,''
{\em Joint International Workshop on Visual Surveillance and Performance Evaluation of Tracking and Surveillance}, 
(\textbf{VSPETS}), 2003, pp.\ 78-85. 

V.\ Rabaud and B.\ Deguine ``A Geometrical Approach To Determine Blackout Windows At Launch,''
AAS/AIAA Space Flight Mechanics Meeting, Ponce, Puerto Rico, (\textbf{AAS}), 2003, 03-187 
