\documentclass{article}

\usepackage[french,english]{babel}
\usepackage{eurosym}
\usepackage{iflang}
\usepackage{resume}

\begin{document}

\selectlanguage{english}

\name{\bf VINCENT RABAUD}

\begin{llist}
\sectiontitle{Education}

\employer{UNIVERSITY OF CALIFORNIA, SAN DIEGO} \location{San Diego, CA, USA}
\dates{01/2004--02/2009}
\IfLanguageName{english}
{
Ph.D. in Computer Science\\
Dissertation: \textit{Manifold Learning Techniques for Non-Rigid Structure from
Motion}.\\
Advisor: Serge Belongie.\\
Research Interests: Structure from Motion, Multiview Geometry, Panorama, Image Manifold Learning, Tracking, Behavior Analysis, Optimization, Visual Captchas, Perception.
}
{
Ph.D. en Informatique Appliqu\'{e}e \`{a} la Vision par Ordinateur\\
Dissertation:\textit{Manifold Learning Techniques for Non-Rigid Structure from
Motion}.\\
Centres d'int\'{e}r\^{e}t: Reconstruction 3D par \'{e}tude de mouvement, Segmentation de mouvement, Tracking, 
Apprentissage de vari\'{e}t\'{e}s, Perception visuelle.\\
Ma\^{i}tre de th\`{e}se: Serge Belongie.
}

\employer{SUPAERO} \location{Toulouse, France}
\dates{09/2001--08/2003}
\IfLanguageName{english}
{
M.S. in Aeronautical and Space Engineering, Space Imagery Major.
}
{
Dipl\^{o}me d'ing\'{e}nieur.
}

\employer{ECOLE POLYTECHNIQUE} \location{Paris, France}
\dates{09/1998--08/2001}
\IfLanguageName{english}
{
B.S./M.S. in Applied Math, Fluid Mechanics and Parallel Computing.
}
{
Dipl\^{o}me d'ing\'{e}nieur.
}

% Research Experience
\IfLanguageName{english}
{
\sectiontitle{Work Experience}
}
{
\sectiontitle{Exp\'{e}rience Professionnelle}
}
\vspace{-0.33cm}

\employer{ALDEBARAN}\location{Paris, France}
\dates{04/2013--now}
\IfLanguageName{english}
{
SW/HW Link Director
\vspace{-0.33cm}
\begin{itemize}
 \item managing two 10-person teams: one focusing on the audio and visual perception of the robot (automated speech 
recognition, text to speech, object recognition, person detection) and one on its movement.
 \item handling the projects definitions, plannings, contracts, execution and participating to the code and technical 
decisions.
 \item since 09/2014, improving relationships between the software and hardware departments by relaying and defining 
the different plannings, decisions and implementations.
\end{itemize}
}
{
Directeur des relations software/hardware.
Manager de l'\'{e}quipe Perception. Interaction Audio/Video, Reconnaissance d'Objets (2d/3d), Reconnaissance/Tracking 
de 
Personne.
}

\employer{OPENCV FOUNDATION\\}
\dates{06/2012--now}
\IfLanguageName{english}
{
Co-Founder and Member of the Board of the official OpenCV library foundation
\vspace{-0.33cm}
\begin{itemize}
 \item representing the OpenCV library in public events.
 \item managing contracts and collaborations (e.g. during Google Summer Of Code).
\end{itemize}
}
{
Co-Fondateur et Membre du Conseil de la fondation \`{a} but non lucratif officielle d'OpenCV.
}

\employer{WILLOW GARAGE}\location{Menlo Park, CA, USA} 
\dates{01/2011--03/2013}
\IfLanguageName{english}
{
Research Engineer
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented new techniques for object recognition based on 2D/3D information.
 \item developed and managed part of the OpenCV library.
 \item worked on several projects related to the Robot Operating System like SLAM, build system, grasping.
\end{itemize}
}
{
Ing\'{e}nieur Chercheur, Reconnaissance d'objets (2d/3d), d\'{e}veloppement et gestion de l'\'{e}quipe 
OpenCV, SLAM, d\'{e}veloppement et maintien de ROS.
}

\employer{VIDEOSURF}\location{San Mateo, CA, USA} 
\dates{03/2009--01/2011}
\IfLanguageName{english}
{
Software Engineer
\vspace{-0.33cm}
\begin{itemize}
 \item developed and implemented algorithms to visually analyze videos from the web using face recognition, video 
summaries and scene analysis.
 \item multiplied by 5 the speed of our processing pipeline up to 200K web videos a day on 30 machines.
\end{itemize}
}
{
Ing\'{e}nieur D\'{e}veloppeur, Reconnaissance faciale, Analyse
Vid\'{e}o.
}

\employer{UNIVERSITY OF CALIFORNIA, SAN DIEGO}\location{La Jolla, CA, USA} 
\dates{01/2004--02/2009}
\IfLanguageName{english}
{
Graduate Student Researcher, Department of Computer Science and Engineering
}
{
Etudiant chercheur, D\'{e}partment d'informatique.
}

\employer{CENTER FOR INTERDISCIPLINARY SCIENCE FOR ART, ARCHITECTURE AND ARCHAEOLOGY (CISA3)}\location{La Jolla, CA, 
USA} 
\dates{06/2007--09/2007}
\IfLanguageName{english}
{
Intern
\vspace{-0.33cm}
\begin{itemize}
 \item with two other persons, designed a robot to scan artist paintings.
 \item created vision algorithms to create on the fly giga-pixel panoramas and visualize them in a web browser.
\end{itemize}
}
{
Stagiaire, Reconstruction automatique de panorama de peinture, Mosa\"{\i}que haute r\'{e}solution.
}

\employer{CALIT2}\location{La Jolla, CA, USA} 
\dates{06/2005--09/2005}
\IfLanguageName{english}
{
Intern, {\em RESCUE} Project
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented algorithms to perform real-time crowd analysis for person counting and movement 
description.
\end{itemize}
}
{
Stagiaire, Etude visuelle de foules humaines, Projet {\em RESCUE}.
}

\employer{UNIVERSITY OF CALIFORNIA, SAN DIEGO}\location{La Jolla, CA, USA} 
\dates{05/2003--12/2004}
\IfLanguageName{english}
{
Intern, {\em Smart Vivarium} Project
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented algorithms to perform automatic analysis of rodent behavior: breathing and sleeping 
frequencies, movement and tracking.
\end{itemize}
}
{
Stagiaire, Groupe de vision par ordinateur, Projet {\em Smart Vivarium}.
}

\employer{CENTRE NATIONAL D'ETUDES SPATIALES (CNES)}\location{Toulouse, France} 
\dates{06/2002--12/2002}
\IfLanguageName{english}
{
Intern, Space Mechanics Department, French Space Agency
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented an algorithm to efficiently and accurately choose the best launch trajectory 
to avoid space debris.
 \item implemented a model of space explosion to study the movement of space debris due to collision.
\end{itemize}
}
{
Stagiaire, D\'{e}partement de M\'{e}canique Spatiale.
}

\employer{OFFICE NATIONAL D'ETUDES ET DE RECHERCHES AEROSPATIALES (ONERA)} \location{Toulouse, France}
\dates{03/2002--06/2002}
\IfLanguageName{english}
{
Intern, Flight Mechanics Department
\vspace{-0.33cm}
\begin{itemize}
 \item proved the optimal position of a glider for optimal fuel efficiency of the plane pulling it in flight.
\end{itemize}
}
{
Stagiare, D\'{e}partement de M\'{e}canique du Vol.
}

\employer{DYNAFLOW-INC} \location{Jessup, MD}
\dates{04/2001--06/2001}
\IfLanguageName{english}
{
Intern, Fluid Mechanics Modeling
\vspace{-0.33cm}
\begin{itemize}
 \item implemented an algorithm to describe the formation of cavities on underwater propellers.
\end{itemize}
}
{
Stagiaire, Mod\'{e}lisation de M\'{e}canique des Fluides.
}

% Teaching Experience
\IfLanguageName{english}
{
\sectiontitle{Teaching Experience}
}
{
\sectiontitle{Exp\'{e}rience Educative}
}
\employer{UNIVERSITY OF CALIFORNIA, SAN DIEGO}\location{La Jolla, CA, USA}
\IfLanguageName{english}
{
CSE252C, {\em Object Recognition}, Fall 2007: Teaching Assistant\\
CSE166, {\em Image Processing}, Fall 2007: Teaching Assistant
}
{
SE252C, {\em Reconnaissance d'objet}, Automne 2007: Assistant de Professeur\\
CSE166, {\em Traitement d'image}, Automne 2007: Assistant de Professeur
}

% Professional Activities
\IfLanguageName{english}
{
\sectiontitle{Professional Activities}

Co-founder and member of the board of the official OpenCV foundation.

Mentor and organizer of Google Summer of Code for OpenCV from 2011 to 2015.

Maintainer/developer of 60+ packages and involved in the core development of the Robot Operating System (ROS).

Reviewer: IEEE International Conference on Computer Vision, IEEE Conference on Computer Vision and Pattern Recognition, 
SIGGRAPH, IEEE Transaction on Pattern Analysis and Machine Intelligence, International Journal of Computer Vision

Organizer of Pixel-Cafe, the weekly vision and graphics seminar at UCSD.

IEEE member, 2005-present
}
{
\sectiontitle{Activit\'{e}s Professionnelles}

Co-fondateur et membre du conseil d'administration de la fondation OpenCV.

Mentor et organisateur de Google Summer of Code pour OpenCV de 2011 \`{a} 2015.

Mainteneur et d\'{e}veloppeur de 60+ paquetages et impliqu\'{e} dans le d\'{e}veloppement du
noyau du Robot Operating System (ROS).

Membre de comit\'{e} de lecture: IEEE International Conference on Computer Vision, IEEE Conference on Computer Vision 
and Pattern Recognition, SIGGRAPH.

Organisateur du Pixel-Cafe, le s\'{e}minaire hebdomadaire de vision et image par ordinateur \`{a} UCSD.

Membre de IEEE.
}

% Skills
\IfLanguageName{english}
{
\sectiontitle{Skills}
Competence: Vision (SfM, web video analysis, image retrieval, object recognition), Robotics, Programming, Architecture, 
Management \\
Programming Languages: C++, Python\\
Programming Libraries: OpenCV, ROS, Boost, OpenMP, TBB, PVM, MPI \\
Extra Interests: Android, Drupal, Matlab, Javascript, PHP, NOSQL \\
Languages: French (native), English (bilingual), Spanish (fluent), Portuguese (beginner), Italian (beginner)
}
{
\sectiontitle{Comp\'{e}tences}
{\em Comp\'{e}tences}: Vision, Robotique, Programmation, Architecte Logiciel, Management\\
{\em Langages de Programmation}: C++, Python\\
{\em Biblioth\`{e}ques Logicielles}: OpenCV, ROS, Boost, OpenMP, TBB, PVM, MPI \\
{\em Autres Int\'{e}r\^{e}ts}: Android, Drupal, Matlab, Javascript, PHP, NOSQL \\
{\em Langues}: Fran\c{c}ais (natif), Anglais (bilingue), Espagnol (fluent), Portugais (d\'{e}butant), Italien
(d\'{e}butant)
}

% Software
\IfLanguageName{english}
{
\sectiontitle{Software}
{\em ROS packages}: maintainer/developer of 60+ ROS packages about computer vision, lasers, graph processing, the NAO 
robot.

{\em Recognition Kitchen}: set of tools to develop and execute object recognition.

{\em Surveillance Video Entertainment System} (SVEN): real-time tracking of pedestrians incorporating appearance 
description, face detection and facial expression analysis.

{\em Painting Panorama}: fast and memory efficient panorama software for very high resolution images of paintings.  Incorporates sparse bundle adjustment, sift and camera auto calibration.

{\em Vincent's Structure from Motion Toolbox for Matlab}: toolbox including many common structure from motion algorithms 
(e.g. rigid, non-rigid, bundle adjustment, visualization).
}
{
\sectiontitle{Logiciels}
{\em Paquetages ROS}: mainteneur et d\'{e}veloppeur de 60+ paquetages ROS de vision par ordinateur, lasers, calcul
en graphe et du robot NAO.

{\em Recognition Kitchen}: ensemble d'outils pour d\'{e}velopper et faire de la reconnaissance d'objet.

{\em Surveillance Video Entertainment System}, (SVEN): logiciel de tracking en temps r\'eel de personnes, incluant un 
descripteur d'apparence, une d\'{e}tection de visage et une analyse d'expression.

{\em Painting Panorama}: logiciel rapide pour fusionner des images en une mosa\"{i}que haute r\'{e}solution.  L'accent 
a \'{e}t\'{e} mis sur l'efficacit\'{e} et la n\'{e}cessit\'{e} de faibles ressources.  Ce logiciel inclut un ajustement 
de faisceaux, les descripteurs SIFT et une calibration automatique.

{\em Vincent's Structure from Motion Toolbox for Matlab}: toolbox pour Matlab incluant plusieurs routines de 
reconstruction 3D (pour un objet rigide, non-rigide, ajustement de faisceaux, calcul d'orientation \dots).
}

% Papers
\IfLanguageName{english}
{
\sectiontitle{Journal Articles}
}
{
\sectiontitle{Articles dans des Revues Internationales}
}
\input{publications_journals.tex}

\IfLanguageName{english}
{
\sectiontitle{Papers in Reviewed Proceedings}
}
{
\sectiontitle{Articles dans des Conf\'{e}rences Internationales}
}
\input{publications_articles.tex}

% Video
\sectiontitle{Video}
M.~Maschion, V.~Rabaud and S.~Belongie, {\em Computer Vision: Fact and Fiction},
Instructional DVD, 2005.

% Papers
%\sectiontitle{Relevant Coursework}
%Computer Vision I (Image Analysis, Radiometry, SFM)\\
%Computer Vision II (Multiple View Geometry)\\
%Computer Vision III (Object Recognition)\\
%Machine Learning\\
%Graphical Models

\sectiontitle{References}

\input{references.tex}

\end{llist}

{\em Last update: \today}

\end{document}
